Superabsorption of light by nanoparticles

### 2015-10-08 2015-Ladutenko-Qabs/submission-nanoscale/comm_template/response-letter/response-letter.tex

When we mix the different sized spheres, there will be an effect of
their mutual interaction. To take this into account, we simulate a
dimer configurations with 0 nm, 10 nm and 30 nm separation between
spheres.  The resulting spectra have a strong contribution from
standalone resonances, while coupling effects seems to be relatively
minor. This can be explained from modal field distribution in
Fig.~4(c) of the manuscript. Positioning spheres in H-k plane we are
exploiting the fact that the fields are highly localized inside the
spheres. Arranging spheres in other planes with respect to incident
polarization, or increasing the number of interacting spheres can
change the effect of coupling. As an example, we tested arrangement of
spheres in E-k plane Fig.~\ref{fig:fdtd}(c); for zero separation the
interaction between spheres is strong, however, due to near-field
nature of this coupling, it rapidly decays with the separation width
Fig.~\ref{fig:fdtd}(d), for separation of 30~nm responses of
individual particles dominate in overall spectra for both planes of
polarization. This way we show that in principle it is possible to
construct an absorption band of an array of dispersed particles simply
optimizing the properties of individual particles.

In order to reflect these findings in the manuscript, we have
rewritten the text from ``As a result, one can design
spectrally-selective absorbers or broadband absorbers with almost
arbitrary prescribed properties.'' to ``As a result, one can design
absorbers with broad spectra or spectrally-selective absorbers with
almost arbitrary prescribed properties.  One can also achieve
broadband performance by mixing particles whose absorption is
optimized for different wavelengths. We have verified that due to the
strong localization of electric dipole field it is possible to design
dimers whose absorbing properties are dominated by the properties of
individual particles, and not by their mutual interaction. As a
result, by appropriately spacing the resonances of individual
particles, their mixture will exhibit a combined broadband
response. Providing such an additional control, this approach
complements the case of self-organized particles of various size and
shape, which was experimentally proven to have a wide absorption
band~[ACS-AMI-Liu-2015]. % Reference to the paper mentioned with the
% reviewer in his second comment.
Further control of the absorption spectrum can be achieved by
arranging our spherical structures in a periodic and non-periodic
arrays.''

### 2015-10-08 2015-Ladutenko-Qabs/submission-nanoscale/comm_template/2015-Ladutenko-Qabs.tex
manuscript text reflow
Synced changes from manuscript to responce letter, text reflow

\footnotetext{\textit{$^{a}$~ITMO University, 49
  Kronverskii Ave., St.~Petersburg 197101, Russian Federation. E-mail: k.ladutenko@metalab.ifmo.ru}}
\footnotetext{\textit{$^{b}$~Ioffe Physical-Technical Institute of the Russian Academy of Sciences, 26 Polytekhnicheskaya Str., St.~Petersburg 194021,
  Russian Federation. }}
\footnotetext{\textit{$^{c}$~Instituto de
  Fusi\'{o}n Nuclear, Universidad Polit\'{e}cnica de Madrid, Jos\'{e}
  Guti\'{e}rrez Abascal 2, E-28006 Madrid, Spain. }}
\footnotetext{\textit{$^{d}$~Nonlinear Physics Centre, Research School of
  Physics and Engineering, The Australian National University, 59
  Mills Rd, Acton, ACT, 2601, Australia. }}

@@

To overcome these limitations, we employ similar approach to the one
used for enhancing scattering cross-section.\cite{Fan-2011} In
particular, we propose to use the multilayer structures, and by means
of stochastic optimization algorithm\cite{Jingqiao-JADE-2009} we
optimize the ACS of such nanoparticles. We analyze the absorption
cross-section of these particles, and present the superabsorption
regime. We further introduce the absorption efficiency, which is the
ACS normalized to the geometric cross-section of particles. The absorption efficiency can be made large either by increasing ACS while keeping the particle size fixed, or by decreasing the particle size for fixed ACS. As a result, we show in this paper that smaller particles are more efficient when they operate in a single mode regime, while larger particles are more efficient absorbers when multiple modes are excited at the same frequency.

>>>>

\footnotetext{\textit{$^{a}$~ITMO University, 49 Kronverskii Ave.,
    St.~Petersburg 197101, Russian Federation. E-mail:
    k.ladutenko@metalab.ifmo.ru}}

\footnotetext{\textit{$^{b}$~Ioffe Physical-Technical Institute of the
    Russian Academy of Sciences, 26 Polytekhnicheskaya Str.,
    St.~Petersburg 194021, Russian Federation. }}
\footnotetext{\textit{$^{c}$~Instituto de Fusi\'{o}n Nuclear,
    Universidad Polit\'{e}cnica de Madrid, Jos\'{e} Guti\'{e}rrez
    Abascal 2, E-28006 Madrid, Spain. }}
\footnotetext{\textit{$^{d}$~Nonlinear Physics Centre, Research School
    of Physics and Engineering, The Australian National University, 59
    Mills Rd, Acton, ACT, 2601, Australia. }}

@@

To overcome these limitations, we employ similar approach to the one
used for enhancing scattering cross-section.\cite{Fan-2011} In
particular, we propose to use the multilayer structures, and by means
of stochastic optimization algorithm\cite{Jingqiao-JADE-2009} we
optimize the ACS of such nanoparticles. We analyze the absorption
cross-section of these particles, and present the superabsorption
regime. We further introduce the absorption efficiency, which is the
ACS normalized to the geometric cross-section of particles.  The
absorption efficiency can be made large either by increasineg ACS while
keeping the particle size fixed, or by decreasing the particle size
for fixed ACS. As a result, we show in this paper that smaller
particles are more efficient when they operate in a single mode
regime, while larger particles are more efficient absorbers when
multiple modes are excited at the same frequency.
